---
title: "Comparing *arima*, *ets* and *OLS* with and without hierarchy process - *Wikipedia Pageviews*"
author: "Mahsa Ashouri"
date: "August 20, 2018"
output: ioslides_presentation
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

#Second case study: "Wikipedia Pageview Data"

## Data description: 
* 913 daily time series (Length of each time series: 394 - 6/1/2016 - 6/1/2017)

* Five hierarchy groups: 

  a. Agent (2 levels - user, spider)
  b. Access (3 levels - desktop, mobile-web, mobile-app)
  c. Purpose (9 levels - blogging  related,  business,  gaming,  general  purpose,  life  style,  photo  sharing,  reunion, travel, video)
  d. Language (4 levels - en (English), de (German), es (Spanish), zh (Chinese))

## Six methods:
a. Forecasting hierarchical time series using **optimal combination reconciliation** with **arima** bottom level forecast
b. Forecasting hierarchical time series using **optimal combination reconciliation** with **ets** bottom level forecast
c. Forecasting hierarchical time series using **optimal combination reconciliation** with **OLS** bottom level forecast
d. Forecasting time series using **arima** models
e. Forecasting time series using **ets** models
f. Forecasting time series using **OLS** models

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
setwd(
  "G:/My Drive/A New Tree based Method for Clustering Time Series/Forecasting paper_Rob/hierarchical-clustering-forecasting/Wikipedia_data"
)
lapply(
  c(
    "quantmod",
    "ggplot2",
    "partykit",
    "scales",
    "matrixStats",
    "MASS",
    "GGally",
    "forecast",
    "dplyr",
    "plyr",
    "reshape",
    "reshape2",
    "gridExtra",
    "stringr",
    "hts",
    "data.table"
  ),
  require,
  character.only = T
)
set.seed(123)
```

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE,eval=FALSE}
##############################
#### Hierarchical Method + ARIMA and ETS
##############################
wikipedia_data_ <-read.csv("wikipedia_data.csv", header = TRUE)
n.series<-length(unique(wikipedia_data_$cat_column))
series_length<-394
wikipedia_data<-as.data.frame(matrix(wikipedia_data_$views,nrow =series_length ,ncol = n.series))
names(wikipedia_data) <-unique(wikipedia_data_$cat_column)
k<-28
n<-nrow(wikipedia_data)
names <- names(wikipedia_data)
##################
## using heirachies and groupings
##################
name_length <- str_length(names)
grouping_hts <- rbind(
  #agent
  str_sub(names, start = name_length - 8, end = name_length - 7),
  #access
  str_sub(names, start = name_length - 15, end = name_length - 9),
  #language
  str_sub(names, start = name_length - 6, end = name_length - 5),
  #purpose
  str_sub(names, start = name_length - 4, end = name_length - 2)
)
total_wikipedia <-
  ts(wikipedia_data,
     start = c(1, 1),
     end=c(1, n),frequency = 7)
validation_wikipedia <-
  window(total_wikipedia,
         start = c(1, ((n-k)+1)),
         end = c(1, n))
ARIMAETSmodel_hierarchy <- function(total_wikipedia) {
  forecast_hierarchy_arima <- list()
  forecast_hierarchy_ets <- list()
  for (i in 1:k) {
    ### training set
    training_wikipedia  <-
      window(total_wikipedia,
             start = c(1, 1),
             end = c(1, (n - k) + (i - 1)))
    ### validation set
    validation_wikipedia <-
      window(total_wikipedia,
             start = c(1, (n - k) + i),
             end = c(1, (n - k) + i))
    g_wikipedia_hts <-
      gts(training_wikipedia, groups = grouping_hts)
    ### running the forecast
    fore_hts_arima <-
      forecast.gts(
        g_wikipedia_hts,
        fmethod = "arima",
        h = 1,
        method = "comb",
        weights = "sd"
      )
    fore_hts_ets <-
      forecast.gts(
        g_wikipedia_hts,
        fmethod = "ets",
        h = 1,
        method = "comb",
        weights = "sd"
      )
    forecast_hierarchy_arima[[length(forecast_hierarchy_arima) + 1]] = as.data.frame(fore_hts_arima$bts)
    forecast_hierarchy_ets[[length(forecast_hierarchy_ets) + 1]] = as.data.frame(fore_hts_ets$bts)
  }
  return(list(forecast_hierarchy_arima, forecast_hierarchy_ets))
}

final_result_hierarchy_arima_ets <-
  ARIMAETSmodel_hierarchy(total_wikipedia)
### saving hierarchy forecast and error results
forecast_hierarchy_arima <-
  do.call("rbind", final_result_hierarchy_arima_ets[[1]])
write.csv(forecast_hierarchy_arima,"forecast_hierarchy_arima_wiki.csv")
forecast_hierarchy_arima[forecast_hierarchy_arima<0]<-0
error_hierarchy_arima <-
  as.data.frame(validation_wikipedia) - forecast_hierarchy_arima
write.csv(error_hierarchy_arima,"error_hierarchy_arima_wiki.csv")
forecast_hierarchy_ets <-
  do.call("rbind", final_result_hierarchy_arima_ets[[2]])
write.csv(forecast_hierarchy_ets,"forecast_hierarchy_ets_wiki.csv")
forecast_hierarchy_ets[forecast_hierarchy_ets<0]<-0
error_hierarchy_ets <-
  as.data.frame(validation_wikipedia) - forecast_hierarchy_ets
write.csv(error_hierarchy_ets,"error_hierarchy_ets_wiki.csv")
##############
#OLS+Hierarchy
##############
## reading data
wikipedia_data_ <-
  read.csv("wikipedia_data.csv", header = TRUE) 
n.series<-length(unique(wikipedia_data_$cat_column))
series_length<-394
wikipedia_data<-as.data.frame(matrix(wikipedia_data_$views,nrow =series_length ,ncol = n.series))
names(wikipedia_data) <-unique(wikipedia_data_$cat_column)
h<-28
n<-nrow(wikipedia_data)
##validation set
validation_set<-wikipedia_data[((n-h)+1):n,]
names <-names(wikipedia_data)
#### group defining
name_length <- str_length(names)
g <- rbind(
  #agent
  str_sub(names, start = name_length - 8, end = name_length - 7),
  #access
  str_sub(names, start = name_length - 15, end = name_length - 9),
  #language
  str_sub(names, start = name_length - 6, end = name_length - 5),
  #purpose
  str_sub(names, start = name_length - 4, end = name_length - 2)
)
gts_wikipedia_data <- gts(wikipedia_data, groups = g)
ally_wikipedia_data <- as.data.frame(aggts(gts_wikipedia_data))
List_2 <- do.call(c, apply(ally_wikipedia_data, 2, list))
OLSmodel<-function(X,freq,k){
  trend<-seq(NROW(X))
  season<-forecast::seasonaldummy(ts(X,frequency = freq))
  Xlag<-quantmod::Lag(X,k=1:freq)
  X_mat<-cbind.data.frame(X,trend,season,Xlag)
  n <- nrow(X_mat)
  fore_base_OLS<-matrix(NA,nrow = k,ncol=1)
  for (i in 1:k) {
    train.1 <- X_mat[1:((n - k) + (i - 1)), ]
    valid.1 <- X_mat[(n - k) + i, ]
    fit <- lm(X ~. , data = train.1)
    fore <- predict.lm( fit , newdata = valid.1)
    fore_base_OLS[i,]<-fore
  }
  return(fore_base_OLS)
}
result_fore_base_hierarchy_OLS<-sapply(List_2, OLSmodel,freq=7,k=28)
View(result_fore_base_hierarchy_OLS)
y.f.recon <-
  combinef(result_fore_base_hierarchy_OLS,
           groups = get_groups(gts_wikipedia_data),
           keep = "gts",
           algorithms = "lu")
forecast_hierarchy_OLS_recon<-as.data.frame(y.f.recon$bts)
View(forecast_hierarchy_OLS_recon)
### matching two data frames order to calculate the errors
#setDT(forecast_hierarchy_OLS_recon)
forecast_hierarchy_OLS_recon<-setcolorder(forecast_hierarchy_OLS_recon, names(validation_set))
write.csv(forecast_hierarchy_OLS_recon,"forecast_hierarchy_OLS_wiki.csv")
forecast_hierarchy_OLS_recon[forecast_hierarchy_OLS_recon<0]<-0
error_hierarchy_OLS_recon<-as.data.frame(validation_set)-as.data.frame(forecast_hierarchy_OLS_recon)
write.csv(error_hierarchy_OLS_recon,"error_hierarchy_OLS_wiki.csv")
```

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
forecast_hierarchy_arima_wiki<-read.csv("forecast_hierarchy_arima_wiki.csv",header = TRUE)
forecast_hierarchy_arima_wiki[forecast_hierarchy_arima_wiki<0]<-0
error_hierarchy_arima_wiki<-read.csv("error_hierarchy_arima_wiki.csv")
forecast_hierarchy_ets_wiki<-read.csv("forecast_hierarchy_ets_wiki.csv",header = TRUE)
forecast_hierarchy_ets_wiki[forecast_hierarchy_ets_wiki<0]<-0
error_hierarchy_ets_wiki<-read.csv("error_hierarchy_ets_wiki.csv")
forecast_hierarchy_OLS_wiki<-read.csv("forecast_hierarchy_OLS_wiki.csv",header = TRUE)
forecast_hierarchy_OLS_wiki[forecast_hierarchy_OLS_wiki<0]<-0
error_hierarchy_OLS_wiki<-read.csv("error_hierarchy_OLS_wiki.csv")
#########################################
#### computing RMSEs and plotting results
########################################
## hierarchy+arima
mean_error_hierarchy_arima_wiki<-apply(error_hierarchy_arima_wiki,2,mean)
RMSE_hierarchy_arima_wiki<-as.data.frame(log(sqrt((mean_error_hierarchy_arima_wiki)^2)))
RMSE_hierarchy_arima_wiki$group<-"Hierarchy-arima"
names(RMSE_hierarchy_arima_wiki)<-c("RMSE","Method")
ave_RMSE_hierarchy_arima_wiki<-mean(as.vector(RMSE_hierarchy_arima_wiki$RMSE)) ##
#hierarchy+ets
mean_error_hierarchy_ets_wiki<-apply(error_hierarchy_ets_wiki,2,mean)
RMSE_hierarchy_ets_wiki<-as.data.frame(log(sqrt((mean_error_hierarchy_ets_wiki)^2)))
RMSE_hierarchy_ets_wiki$group<-"Hierarchy-ets"
names(RMSE_hierarchy_ets_wiki)<-c("RMSE","Method")
ave_RMSE_hierarchy_ets_wiki<-mean(as.vector(RMSE_hierarchy_ets_wiki$RMSE)) ##
#hierarchy+OLS
mean_error_hierarchy_OLS_wiki<-apply(error_hierarchy_OLS_wiki,2,mean) 
RMSE_hierarchy_OLS_wiki<-as.data.frame(log(sqrt((mean_error_hierarchy_OLS_wiki)^2)))
RMSE_hierarchy_OLS_wiki$group<-"Hierarchy-OLS"
names(RMSE_hierarchy_OLS_wiki)<-c("RMSE","Method")
ave_RMSE_hierarchy_OLS_wiki<-mean(as.vector(RMSE_hierarchy_OLS_wiki$RMSE)) ## 

Long_RMSE_hierarchy_wiki<-rbind(RMSE_hierarchy_arima_wiki,RMSE_hierarchy_ets_wiki,RMSE_hierarchy_OLS_wiki)

long_error_hierarchy_arima_wiki<-melt(error_hierarchy_arima_wiki)
long_error_hierarchy_arima_wiki$Method<-"Hierarchy-arima"
names(long_error_hierarchy_arima_wiki)<-c("Series","Error","Method")
long_error_hierarchy_ets_wiki<-melt(error_hierarchy_ets_wiki)
long_error_hierarchy_ets_wiki$Method<-"Hierarchy-ets"
names(long_error_hierarchy_ets_wiki)<-c("Series","Error","Method")
long_error_hierarchy_OLS_wiki<-melt(error_hierarchy_OLS_wiki)
long_error_hierarchy_OLS_wiki$Mrthod<-"Hierarchy-OLS"
names(long_error_hierarchy_OLS_wiki)<-c("Series","Error","Method")
Long_Error_hierarchy_wiki<-rbind(long_error_hierarchy_arima_wiki,long_error_hierarchy_ets_wiki,long_error_hierarchy_OLS_wiki)

```

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE,eval=FALSE}
##############################
#### Method + ARIMA and ETS
##############################
wikipedia_data_ <-read.csv("wikipedia_data.csv", header = TRUE)
n.series<-length(unique(wikipedia_data_$cat_column))
series_length<-394
wikipedia_data<-as.data.frame(matrix(wikipedia_data_$views,nrow =series_length ,ncol = n.series))
names(wikipedia_data) <-unique(wikipedia_data_$cat_column)
k<-28
n<-nrow(wikipedia_data)
List_1 <- do.call(c, apply(wikipedia_data, 2, list))
ARIMAETSmodel <- function(df) {
  error_arima <- list()
  forecast_arima <- list()
  error_ets<-list()
  forecast_ets<-list()
  for (i in 1:k) {
    n <- length(df)
    simulated_series.ts <- ts(df,
                              start = c(1, 1),
                              end = c(1, n),
                              freq = 7)
    train.ts <-
      window(simulated_series.ts, end = c(1, (n - k) + (i - 1)))
    valid.ts <-
      window(simulated_series.ts,
             start = c(1, (n - k) + i),
             end = c(1, (n - k) + i))
    #### forecast and error
    fit_arima <- auto.arima(train.ts)
    pred_arima <- forecast(fit_arima, h = 1)
    fore_arima<-pred_arima$mean
    forecast_arima[[length(forecast_arima) + 1]] = as.data.frame(fore_arima)
    fore_arima[fore_arima<0]<-0
    error_arima_ <-
      as.numeric(valid.ts)- as.numeric(fore_arima)
    error_arima[[length(error_arima) + 1]] = as.data.frame(error_arima_)
    fit_ets <- ets(train.ts)
    pred_ets <- forecast(fit_ets, h = 1)
    fore_ets<-pred_ets$mean
    fore_ets[fore_ets<0]<-0
    forecast_ets[[length(forecast_ets) + 1]] = as.data.frame(fore_ets)
    error_ets_ <-
      as.numeric(valid.ts)- as.numeric(fore_ets)
    error_ets[[length(error_ets) + 1]] = as.data.frame(error_ets_)
  }
  return(list(forecast_arima, error_arima,forecast_ets,error_ets))
}

forecast_error_result_arima_ets = lapply(List_1, ARIMAETSmodel) 
##### forecast arima
List_forecast_arima <- list()
for (i in 1:n.series) {
  List_forecast_arima[[length(List_forecast_arima) + 1]] = ldply (forecast_error_result_arima_ets[[i]][1], data.frame)
}
fore_arima<-unlist(List_forecast_arima)
forecast_arima<-as.data.frame(matrix(fore_arima,nrow=k,ncol=n.series))
names(forecast_arima) <-as.vector(names(forecast_error_result_arima_ets))
## error arima
List_error_arima <- list()
for (i in 1:n.series) {
  List_error_arima[[length(List_error_arima) + 1]] = ldply (forecast_error_result_arima_ets[[i]][2], data.frame)
}
er_arima<-unlist(List_error_arima)
error_arima<-as.data.frame(matrix(er_arima,nrow=k,ncol=n.series))
names(error_arima) <-as.vector(names(forecast_error_result_arima_ets))
##### forecast ets
List_forecast_ets <- list()
for (i in 1:n.series) {
  List_forecast_ets[[length(List_forecast_ets) + 1]] = ldply (forecast_error_result_arima_ets[[i]][3], data.frame)
}
fore_ets<-unlist(List_forecast_ets)
forecast_ets<-as.data.frame(matrix(fore_ets,nrow=k,ncol=n.series))
names(forecast_ets) <-as.vector(names(forecast_error_result_arima_ets))
## error ets
List_error_ets <- list()
for (i in 1:n.series) {
  List_error_ets[[length(List_error_ets) + 1]] = ldply (forecast_error_result_arima_ets[[i]][4], data.frame)
}
er_ets<-unlist(List_error_ets)
error_ets<-as.data.frame(matrix(er_ets,nrow=k,ncol=n.series))
names(error_ets) <-as.vector(names(forecast_error_result_arima_ets))
## saving results
write.csv(forecast_arima,"forecast_arima_wiki.csv")
write.csv(error_arima,"error_arima_wiki.csv")
write.csv(forecast_ets,"forecast_ets_wiki.csv")
write.csv(error_ets,"error_ets_wiki.csv")

##########
#### OLS
#########
wikipedia_data_ <-
  read.csv("wikipedia_data.csv", header = TRUE)
n.series<-length(unique(wikipedia_data_$cat_column))
series_length<-394
wikipedia_data<-as.data.frame(matrix(wikipedia_data_$views,nrow =series_length ,ncol = n.series))
names(wikipedia_data) <-unique(wikipedia_data_$cat_column)
h<-28
n<-nrow(wikipedia_data)
validation_set<-wikipedia_data[((n-h)+1):n,]
List_1 <- do.call(c, apply(wikipedia_data, 2, list))
OLSmodel<-function(X,freq,h){
  trend<-seq(NROW(X))
  season<-forecast::seasonaldummy(ts(X,frequency = freq))
  Xlag<-quantmod::Lag(X,k=1:freq)
  X_mat<-cbind.data.frame(X,trend,season,Xlag)
  n <- nrow(X_mat)
  fore_OLS<-matrix(NA,nrow = h,ncol=1)
   for (i in 1:h) {
    train.1 <- X_mat[1:((n - h) + (i - 1)), ]
    valid.1 <- X_mat[(n - h) + i, ]
    fit <- lm(X ~. , data = train.1)
    fore <- predict.lm( fit , newdata = valid.1)
    fore_OLS[i,]<-fore
  }
  return(fore_OLS)
}

result_fore_OLS<-as.data.frame(sapply(List_1, OLSmodel,freq=7,h=28))
### matching two data frames order to calculate the errors
#setDT(result_fore_OLS)
forecast_OLS<-setcolorder(result_fore_OLS, names(validation_set))
write.csv(forecast_OLS,"forecast_OLS_wiki.csv")
forecast_OLS[forecast_OLS<0]<-0
error_OLS<-validation_set-forecast_OLS
write.csv(error_OLS,"error_OLS_wiki.csv")
```

```{r echo=FALSE, message = FALSE, results='asis',cache=TRUE}
forecast_arima_wiki<-read.csv("forecast_arima_wiki.csv",header = TRUE)
forecast_arima_wiki[forecast_arima_wiki<0]<-0
error_arima_wiki<-read.csv("error_arima_wiki.csv")
forecast_ets_wiki<-read.csv("forecast_ets_wiki.csv",header = TRUE)
forecast_ets_wiki[forecast_ets_wiki<0]<-0
error_ets_wiki<-read.csv("error_ets_wiki.csv")
forecast_OLS_wiki<-read.csv("forecast_OLS_wiki.csv",header = TRUE)
forecast_OLS_wiki[forecast_OLS_wiki<0]<-0
error_OLS_wiki<-read.csv("error_OLS_wiki.csv")

mean_error_arima_wiki<-apply(error_arima_wiki,2,mean)
RMSE_arima_wiki<-as.data.frame(log(sqrt((mean_error_arima_wiki)^2)))
RMSE_arima_wiki$group<-"arima"
names(RMSE_arima_wiki)<-c("RMSE","Method")
ave_RMSE_arima_wiki<-mean(as.vector(RMSE_arima_wiki$RMSE)) ##

mean_error_ets_wiki<-apply(error_ets_wiki,2,mean)
RMSE_ets_wiki<-as.data.frame(log(sqrt((mean_error_ets_wiki)^2)))
RMSE_ets_wiki$group<-"ets"
names(RMSE_ets_wiki)<-c("RMSE","Method")
ave_RMSE_ets_wiki<-mean(as.vector(RMSE_ets_wiki$RMSE)) ##

mean_error_OLS_wiki<-apply(error_OLS_wiki,2,mean)
RMSE_OLS_wiki<-as.data.frame(log(sqrt((mean_error_OLS_wiki)^2)))
RMSE_OLS_wiki$group<-"OLS"
names(RMSE_OLS_wiki)<-c("RMSE","Method")
ave_RMSE_OLS_wiki<-mean(as.vector(RMSE_OLS_wiki$RMSE)) ##

Long_RMSE_arima_wiki<-rbind(RMSE_hierarchy_arima_wiki,RMSE_arima_wiki)
Long_RMSE_ets_wiki<-rbind(RMSE_hierarchy_ets_wiki,RMSE_ets_wiki)
Long_RMSE_OLS_wiki<-rbind(RMSE_hierarchy_OLS_wiki,RMSE_OLS_wiki)
Long_RMSE_wiki<-rbind(RMSE_arima_wiki,RMSE_ets_wiki,RMSE_OLS_wiki)
Long_RMSE_all_wiki<-rbind(RMSE_arima_wiki,RMSE_hierarchy_arima_wiki,RMSE_ets_wiki,RMSE_hierarchy_ets_wiki,RMSE_OLS_wiki,RMSE_hierarchy_OLS_wiki)

long_error_arima_wiki<-melt(error_arima_wiki)
long_error_arima_wiki$Method<-"arima"
names(long_error_arima_wiki)<-c("Series","Error","Method")
long_error_ets_wiki<-melt(error_ets_wiki)
long_error_ets_wiki$Method<-"ets"
names(long_error_ets_wiki)<-c("Series","Error","Method")
long_error_OLS_wiki<-melt(error_OLS_wiki)
long_error_OLS_wiki$Mrthod<-"OLS"
names(long_error_OLS_wiki)<-c("Series","Error","Method")

Long_Error_arima_wiki<-rbind(long_error_hierarchy_arima_wiki,long_error_arima_wiki)
Long_Error_ets_wiki<-rbind(long_error_hierarchy_ets_wiki,long_error_ets_wiki)
Long_Error_OLS_wiki<-rbind(long_error_hierarchy_OLS_wiki,long_error_OLS_wiki)
Long_Erro_wiki<-rbind(long_error_arima_wiki,long_error_ets_wiki,long_error_OLS_wiki)
Long_Error_all_wiki<-rbind(long_error_arima_wiki,long_error_hierarchy_arima_wiki,
                      long_error_ets_wiki,long_error_hierarchy_ets_wiki,
                      long_error_OLS_wiki,long_error_hierarchy_OLS_wiki)
```

## WikipediaData: Comparing all methods - with and without hierarchy - mean(log(RMSE))

```{r echo=FALSE, message = FALSE, results='asis',cache=TRUE}
library(knitr)
library(kableExtra)
ave_RMSE_arima_wiki<-round(ave_RMSE_arima_wiki,3)
ave_RMSE_hierarchy_arima_wiki<-round(ave_RMSE_hierarchy_arima_wiki,3)
ave_RMSE_ets_wiki<-round(ave_RMSE_ets_wiki,3)
ave_RMSE_hierarchy_ets_wiki<-round(ave_RMSE_hierarchy_ets_wiki,3)
ave_RMSE_OLS_wiki<-round(ave_RMSE_OLS_wiki,3)
ave_RMSE_hierarchy_OLS_wiki<-round(ave_RMSE_hierarchy_OLS_wiki,3)
table1<-matrix(NA,nrow=6,ncol=2)
colnames(table1)<-c("Method","Mean(log(RMSE))")
table1[,1]<-c("arima","Hierarchy-arima","ets","Hierarchy-ets","OLS","Hierarchy-OLS")
table1[,2]<-c(ave_RMSE_arima_wiki,ave_RMSE_hierarchy_arima_wiki,
             ave_RMSE_ets_wiki,ave_RMSE_hierarchy_ets_wiki,
             ave_RMSE_OLS_wiki,ave_RMSE_hierarchy_OLS_wiki)
kable(table1, align =c('c','c'),format = "pandoc") 
```

## WikipediaData: Comparing three hierarchy methods - log(RMSE) Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot log(RMSE)
ggplot() +
  geom_density(data = Long_RMSE_hierarchy_wiki, aes(x = (RMSE), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-10, 10)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three hierarchy methods - log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot log(RMSE)
ggplot() +
  geom_boxplot(data = Long_RMSE_hierarchy_wiki,
               aes(x = Method, y = (RMSE), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three hierarchy methods - Subtracted log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
RMSE_hierarchy_arima_wiki<-RMSE_hierarchy_arima_wiki[match(rownames(RMSE_hierarchy_ets_wiki), rownames(RMSE_hierarchy_arima_wiki)), ]
subtract_hierarchy_arima_ets_RMSE_wiki<-as.data.frame(RMSE_hierarchy_arima_wiki$RMSE - RMSE_hierarchy_ets_wiki$RMSE)
subtract_hierarchy_arima_ets_RMSE_wiki$Method<-"Sub-Hierarchy-arima-ets-RMSE"
names(subtract_hierarchy_arima_ets_RMSE_wiki)<-c("sublog(RMSE)","Method")

RMSE_hierarchy_arima<-RMSE_hierarchy_arima_wiki[match(rownames(RMSE_hierarchy_OLS_wiki), rownames(RMSE_hierarchy_arima_wiki)), ]
subtract_hierarchy_arima_OLS_RMSE_wiki<-as.data.frame(RMSE_hierarchy_arima_wiki$RMSE - RMSE_hierarchy_OLS_wiki$RMSE)
subtract_hierarchy_arima_OLS_RMSE_wiki$Method<-"Sub-Hierarchy-arima-OLS-RMSE"
names(subtract_hierarchy_arima_OLS_RMSE_wiki)<-c("sublog(RMSE)","Method")

RMSE_hierarchy_ets<-RMSE_hierarchy_ets_wiki[match(rownames(RMSE_hierarchy_OLS_wiki), rownames(RMSE_hierarchy_ets_wiki)), ]
subtract_hierarchy_ets_OLS_RMSE_wiki<-as.data.frame(RMSE_hierarchy_ets_wiki$RMSE - RMSE_hierarchy_OLS_wiki$RMSE)
subtract_hierarchy_ets_OLS_RMSE_wiki$Method<-"Sub-Hierarchy-ets-OLS-RMSE"
names(subtract_hierarchy_ets_OLS_RMSE_wiki)<-c("sublog(RMSE)","Method")

Long_subtract_hierarchy_arima_ets_OLS_RMSE_wiki<-rbind(subtract_hierarchy_arima_ets_RMSE_wiki,subtract_hierarchy_arima_OLS_RMSE_wiki,subtract_hierarchy_ets_OLS_RMSE_wiki)

ggplot() +
  geom_boxplot(data = Long_subtract_hierarchy_arima_ets_OLS_RMSE_wiki,
               aes(x = Method , y = (Long_subtract_hierarchy_arima_ets_OLS_RMSE_wiki$`sublog(RMSE)`), 
                   fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )

```

## WikipediaData: Comparing three hierarchy methods - Error Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot Error
ggplot() +
  geom_density(data = Long_Error_hierarchy_wiki , aes(x = (Error), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-40, 40)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three hierarchy methods - Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot Error
ggplot() +
  geom_boxplot(data = Long_Error_hierarchy_wiki,
               aes(x = Method, y = (Error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three hierarchy methods - Subtracted Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
cols_hierarchy_arima_ets_wiki <- sort(intersect(names(error_hierarchy_arima_wiki), names(error_hierarchy_ets_wiki)))
subtract_hierarchy_arima_ets_wiki<-error_hierarchy_arima_wiki[cols_hierarchy_arima_ets_wiki] - error_hierarchy_ets_wiki[cols_hierarchy_arima_ets_wiki]
long_subtract_hierarchy_arima_ets_wiki<-melt(subtract_hierarchy_arima_ets_wiki)
long_subtract_hierarchy_arima_ets_wiki$Method<-"Sub-Hierarchy-arima-ets"
names(long_subtract_hierarchy_arima_ets_wiki)<-c("Series","subtracted_error","Method")

cols_hierarchy_arima_OLS_wiki <- sort(intersect(names(error_hierarchy_arima_wiki), names(error_hierarchy_OLS_wiki)))
subtract_hierarchy_arima_OLS_wiki<-error_hierarchy_arima_wiki[cols_hierarchy_arima_OLS_wiki] - error_hierarchy_OLS_wiki[cols_hierarchy_arima_OLS_wiki]
long_subtract_hierarchy_arima_OLS_wiki<-melt(subtract_hierarchy_arima_OLS_wiki)
long_subtract_hierarchy_arima_OLS_wiki$Method<-"Sub-Hierarchy-arima-OLS"
names(long_subtract_hierarchy_arima_OLS_wiki)<-c("Series","subtracted_error","Method")

cols_hierarchy_ets_OLS_wiki <- sort(intersect(names(error_hierarchy_ets_wiki), names(error_hierarchy_OLS_wiki)))
subtract_hierarchy_ets_OLS_wiki<-error_hierarchy_ets_wiki[cols_hierarchy_ets_OLS_wiki] - error_hierarchy_OLS_wiki[cols_hierarchy_ets_OLS_wiki]
long_subtract_hierarchy_ets_OLS_wiki<-melt(subtract_hierarchy_ets_OLS_wiki)
long_subtract_hierarchy_ets_OLS_wiki$Method<-"Sub-Hierarchy-ets-OLS"
names(long_subtract_hierarchy_ets_OLS_wiki)<-c("Series","subtracted_error","Method")

Long_subtract_hierarchy_arima_ets_OLS_wiki<-rbind(long_subtract_hierarchy_arima_ets_wiki,long_subtract_hierarchy_arima_OLS_wiki,long_subtract_hierarchy_ets_OLS_wiki)

ggplot() +
  geom_boxplot(data = Long_subtract_hierarchy_arima_ets_OLS_wiki,
               aes(x = Method, y = (subtracted_error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three hierarchy methods - Forecasted Series Plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE, fig.width=8.3, fig.height=5}
wikipedia_data <-read.csv("wikipedia_data.csv", header = TRUE) 
long_wikipedia_data<-cbind.data.frame(wikipedia_data$cat_column,wikipedia_data$views,wikipedia_data$Split)
names(long_wikipedia_data)<-c("category","views","Method")
m<-split.data.frame(long_wikipedia_data,long_wikipedia_data$Method)
long_wikipedia_data<-as.data.frame(m[[2]])
long_wikipedia_data$Time<-rep(1:28,913)

long_forecast_hierarchy_arima_wiki<-melt(forecast_hierarchy_arima_wiki)
long_forecast_hierarchy_arima_wiki$Method<-"Hierarchy_arima"
names(long_forecast_hierarchy_arima_wiki)<-c("category","views","Method")
long_forecast_hierarchy_arima_wiki$Time<-rep(1:28,913)

long_forecast_hierarchy_OLS_wiki<-melt(forecast_hierarchy_OLS_wiki)
long_forecast_hierarchy_OLS_wiki$Method<-"Hierarchy_OLS"
names(long_forecast_hierarchy_OLS_wiki)<-c("category","views","Method")
long_forecast_hierarchy_OLS_wiki$Time<-rep(1:28,913)

long_forecast_hierarchy_ets_wiki<-melt(forecast_hierarchy_ets_wiki)
long_forecast_hierarchy_ets_wiki$Method<-"Hierarchy_ets"
names(long_forecast_hierarchy_ets_wiki)<-c("category","views","Method")
long_forecast_hierarchy_ets_wiki$Time<-rep(1:28,913)

long_forecast_hierarchy_wiki<-rbind(long_wikipedia_data,long_forecast_hierarchy_arima_wiki,long_forecast_hierarchy_ets_wiki,long_forecast_hierarchy_OLS_wiki)

long_forecast_hierarchy_split_wiki<-split.data.frame(long_forecast_hierarchy_wiki,long_forecast_hierarchy_wiki$category)
sample_series_hierarchy_wiki<-rbind.data.frame(long_forecast_hierarchy_split_wiki[[1]],long_forecast_hierarchy_split_wiki[[100]],                                       long_forecast_hierarchy_split_wiki[[200]],long_forecast_hierarchy_split_wiki[[300]],
                  long_forecast_hierarchy_split_wiki[[400]],
                  long_forecast_hierarchy_split_wiki[[500]]
                  
                  )

ggplot(sample_series_hierarchy_wiki, aes(x = Time, y = views, color = Method)) + geom_line(size=1) + 
  scale_colour_manual(values=c(validation='black', Hierarchy_arima='blue', Hierarchy_ets='green', Hierarchy_OLS='red'))+
  facet_wrap( ~ category, ncol = 3,scales = 'free')+ 
theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom")

```

## WikipediaData: Comparing three methods - without hierarchy - log(RMSE) Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot log(RMSE)
ggplot() +
  geom_density(data = Long_RMSE_wiki, aes(x = (RMSE), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-10, 10)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three methods - without hierarchy - log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot log(RMSE)
ggplot() +
  geom_boxplot(data = Long_RMSE_wiki,
               aes(x = Method, y = (RMSE), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three methods - without hierarchy - Subtracted log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
RMSE_arima_wiki<-RMSE_arima_wiki[match(rownames(RMSE_ets_wiki), rownames(RMSE_arima_wiki)), ]
subtract_arima_ets_RMSE_wiki<-as.data.frame(RMSE_arima_wiki$RMSE - RMSE_ets_wiki$RMSE)
subtract_arima_ets_RMSE_wiki$Method<-"Sub-arima-ets-RMSE"
names(subtract_arima_ets_RMSE_wiki)<-c("sublog(RMSE)","Method")

RMSE_arima_wiki<-RMSE_arima_wiki[match(rownames(RMSE_OLS_wiki), rownames(RMSE_arima_wiki)), ]
subtract_arima_OLS_RMSE_wiki<-as.data.frame(RMSE_arima_wiki$RMSE - RMSE_OLS_wiki$RMSE)
subtract_arima_OLS_RMSE_wiki$Method<-"Sub-arima-OLS-RMSE"
names(subtract_arima_OLS_RMSE_wiki)<-c("sublog(RMSE)","Method")

RMSE_ets_wiki<-RMSE_ets_wiki[match(rownames(RMSE_OLS_wiki), rownames(RMSE_ets_wiki)), ]
subtract_ets_OLS_RMSE_wiki<-as.data.frame(RMSE_ets_wiki$RMSE - RMSE_OLS_wiki$RMSE)
subtract_ets_OLS_RMSE_wiki$Method<-"Sub-ets-OLS-RMSE"
names(subtract_ets_OLS_RMSE_wiki)<-c("sublog(RMSE)","Method")

Long_subtract_arima_ets_OLS_RMSE_wiki<-rbind(subtract_arima_ets_RMSE_wiki,subtract_arima_OLS_RMSE_wiki,subtract_ets_OLS_RMSE_wiki)

ggplot() +
  geom_boxplot(data = Long_subtract_arima_ets_OLS_RMSE_wiki,
               aes(x = Method , y = (Long_subtract_arima_ets_OLS_RMSE_wiki$`sublog(RMSE)`), 
                   fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three methods - without hierarchy - Error Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot Error
ggplot() +
  geom_density(data = Long_Erro_wiki, aes(x = (Error), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-40, 40)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three methods - without hierarchy - Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot Error
ggplot() +
  geom_boxplot(data = Long_Erro_wiki,
               aes(x = Method, y = (Error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three methods - without hierarchy- Subtracted Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
cols_arima_ets_wiki <- sort(intersect(names(error_arima_wiki), names(error_ets_wiki)))
subtract_arima_ets_wiki<-error_arima_wiki[cols_arima_ets_wiki] - error_ets_wiki[cols_arima_ets_wiki]
long_subtract_arima_ets_wiki<-melt(subtract_arima_ets_wiki)
long_subtract_arima_ets_wiki$Method<-"Sub-arima-ets"
names(long_subtract_arima_ets_wiki)<-c("Series","subtracted_error","Method")

cols_arima_OLS_wiki <- sort(intersect(names(error_arima_wiki), names(error_OLS_wiki)))
subtract_arima_OLS_wiki<-error_arima_wiki[cols_arima_OLS_wiki] - error_OLS_wiki[cols_arima_OLS_wiki]
long_subtract_arima_OLS_wiki<-melt(subtract_arima_OLS_wiki)
long_subtract_arima_OLS_wiki$Method<-"Sub-arima-OLS"
names(long_subtract_arima_OLS_wiki)<-c("Series","subtracted_error","Method")

cols_ets_OLS_wiki <- sort(intersect(names(error_ets_wiki), names(error_OLS_wiki)))
subtract_ets_OLS_wiki<-error_ets_wiki[cols_ets_OLS_wiki] - error_OLS_wiki[cols_ets_OLS_wiki]
long_subtract_ets_OLS_wiki<-melt(subtract_ets_OLS_wiki)
long_subtract_ets_OLS_wiki$Method<-"Sub-ets-OLS"
names(long_subtract_ets_OLS_wiki)<-c("Series","subtracted_error","Method")

Long_subtract_arima_ets_OLS_wiki<-rbind(long_subtract_arima_ets_wiki,long_subtract_arima_OLS_wiki,long_subtract_ets_OLS_wiki)

ggplot() +
  geom_boxplot(data = Long_subtract_arima_ets_OLS_wiki,
               aes(x = Method, y = (subtracted_error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing three methods - without hierarchy - Forecasted Series Plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE, fig.width=8.3, fig.height=5}
long_forecast_arima_wiki<-melt(forecast_arima_wiki)
long_forecast_arima_wiki$Method<-"arima"
names(long_forecast_arima_wiki)<-c("category","views","Method")
long_forecast_arima_wiki$Time<-rep(1:28,913)

long_forecast_OLS_wiki<-melt(forecast_OLS_wiki)
long_forecast_OLS_wiki$Method<-"OLS"
names(long_forecast_OLS_wiki)<-c("category","views","Method")
long_forecast_OLS_wiki$Time<-rep(1:28,913)

long_forecast_ets_wiki<-melt(forecast_ets_wiki)
long_forecast_ets_wiki$Method<-"ets"
names(long_forecast_ets_wiki)<-c("category","views","Method")
long_forecast_ets_wiki$Time<-rep(1:28,913)

long_forecast_wiki<-rbind(long_wikipedia_data,long_forecast_arima_wiki,long_forecast_ets_wiki,long_forecast_OLS_wiki)

long_forecast_split_wiki<-split.data.frame(long_forecast_wiki,long_forecast_wiki$category)
sample_series_wiki<-rbind.data.frame(long_forecast_split_wiki[[1]],long_forecast_split_wiki[[100]],long_forecast_split_wiki[[200]],long_forecast_split_wiki[[300]],
                  long_forecast_split_wiki[[400]],
                  long_forecast_split_wiki[[500]]
                                    )

ggplot(sample_series_wiki, aes(x = Time, y = views, color = Method)) + geom_line(size=1) + 
  scale_colour_manual(values=c(validation='black', arima='blue', ets='green', OLS='red'))+
  facet_wrap( ~ category, ncol = 3,scales = 'free')+theme(text  = element_text(size = 12),legend.direction = "horizontal",
    legend.position = "bottom")

```

## WikipediaData: Comparing arima methods - with and without hierarchy - log(RMSE) Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot log(RMSE)
ggplot() +
  geom_density(data = Long_RMSE_arima_wiki, aes(x = (RMSE), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-10, 10)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing arima methods - with and without hierarchy - log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot log(RMSE)
ggplot() +
  geom_boxplot(data = Long_RMSE_arima_wiki,
               aes(x = Method, y = (RMSE), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing arima methods - with and without hierarchy - Subtracted log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
RMSE_arima_wiki<-RMSE_arima_wiki[match(rownames(RMSE_arima_wiki), rownames(RMSE_hierarchy_arima_wiki)), ]
subtract_hierarchy_arima_arima_RMSE_wiki<-as.data.frame(RMSE_arima_wiki$RMSE - RMSE_hierarchy_arima_wiki$RMSE)
subtract_hierarchy_arima_arima_RMSE_wiki$Method<-"Sub-Hierarchy-arima-arima-RMSE"
names(subtract_hierarchy_arima_arima_RMSE_wiki)<-c("sublog(RMSE)","Method")

ggplot() +
  geom_boxplot(data = subtract_hierarchy_arima_arima_RMSE_wiki,
               aes(x = Method , y = (subtract_hierarchy_arima_arima_RMSE_wiki$`sublog(RMSE)`), 
                   fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing arima methods - with and without hierarchy - Error Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot Error
ggplot() +
  geom_density(data = Long_Error_arima_wiki , aes(x = (Error), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-40, 40)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing arima methods - with and without hierarchy - Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot Error
ggplot() +
  geom_boxplot(data = Long_Error_arima_wiki,
               aes(x = Method, y = (Error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing arima methods - with and without hierarchy - Subtracted Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
cols_arima_arima_hierarchy_wiki <- sort(intersect(names(error_arima_wiki), names(error_hierarchy_arima_wiki)))
subtract_arima_arima_hierarchy_wiki<-error_arima_wiki[cols_arima_arima_hierarchy_wiki] - error_hierarchy_arima_wiki[cols_arima_arima_hierarchy_wiki]
long_subtract_arima_arima_hierarchy_wiki<-melt(subtract_arima_arima_hierarchy_wiki)
long_subtract_arima_arima_hierarchy_wiki$Method<-"Sub-arima-hierarchy-arima"
names(long_subtract_arima_arima_hierarchy_wiki)<-c("Series","subtracted_error","Method")

ggplot() +
  geom_boxplot(data = long_subtract_arima_arima_hierarchy_wiki,
               aes(x = Method, y = (subtracted_error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing arima methods - with and without hierarchy - Forecasted Series Plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE, fig.width=8.3, fig.height=5}
long_forecast_arima_wiki<-rbind(long_wikipedia_data,long_forecast_arima_wiki,long_forecast_hierarchy_arima_wiki)

long_forecast_arima_split_wiki<-split.data.frame(long_forecast_arima_wiki,long_forecast_arima_wiki$category)
sample_series_arima_wiki<-rbind.data.frame(long_forecast_arima_split_wiki[[1]],long_forecast_arima_split_wiki[[100]],long_forecast_arima_split_wiki[[200]],long_forecast_arima_split_wiki[[300]],long_forecast_arima_split_wiki[[400]],
                  long_forecast_arima_split_wiki[[500]]
                                    )

ggplot(sample_series_arima_wiki, aes(x = Time, y = views, color = Method)) + geom_line(size=1) + 
  scale_colour_manual(values=c(validation='black', arima='blue', Hierarchy_arima='green'))+
  facet_wrap( ~ category, ncol = 3,scales = 'free')+theme(text  = element_text(size = 12),legend.direction = "horizontal",
    legend.position = "bottom")

```

## WikipediaData: Comparing ets methods - with and without hierarchy - log(RMSE) Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot log(RMSE)
ggplot() +
  geom_density(data = Long_RMSE_ets_wiki, aes(x = (RMSE), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-10, 10)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot log(RMSE)
ggplot() +
  geom_boxplot(data = Long_RMSE_ets_wiki,
               aes(x = Method, y = (RMSE), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - Subtracted log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
RMSE_ets_wiki<-RMSE_ets_wiki[match(rownames(RMSE_ets_wiki), rownames(RMSE_hierarchy_ets_wiki)), ]
subtract_hierarchy_ets_ets_RMSE_wiki<-as.data.frame(RMSE_ets_wiki$RMSE - RMSE_hierarchy_ets_wiki$RMSE)
subtract_hierarchy_ets_ets_RMSE_wiki$Method<-"Sub-Hierarchy-ets-ets-RMSE"
names(subtract_hierarchy_ets_ets_RMSE_wiki)<-c("sublog(RMSE)","Method")

ggplot() +
  geom_boxplot(data = subtract_hierarchy_ets_ets_RMSE_wiki,
               aes(x = Method , y = (subtract_hierarchy_ets_ets_RMSE_wiki$`sublog(RMSE)`), 
                   fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - Error Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot Error
ggplot() +
  geom_density(data = Long_Error_ets_wiki , aes(x = (Error), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-40, 40)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot Error
ggplot() +
  geom_boxplot(data = Long_Error_ets_wiki,
               aes(x = Method, y = (Error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - Subtracted Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
cols_ets_ets_hierarchy_wiki <- sort(intersect(names(error_ets_wiki), names(error_hierarchy_ets_wiki)))
subtract_ets_ets_hierarchy_wiki<-error_ets_wiki[cols_ets_ets_hierarchy_wiki] - error_hierarchy_ets_wiki[cols_ets_ets_hierarchy_wiki]
long_subtract_ets_ets_hierarchy_wiki<-melt(subtract_ets_ets_hierarchy_wiki)
long_subtract_ets_ets_hierarchy_wiki$Method<-"Sub-ets-hierarchy-ets"
names(long_subtract_ets_ets_hierarchy_wiki)<-c("Series","subtracted_error","Method")

ggplot() +
  geom_boxplot(data = long_subtract_ets_ets_hierarchy_wiki,
               aes(x = Method, y = (subtracted_error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - Forecasted Series Plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE, fig.width=8.3, fig.height=5}
long_forecast_ets_wiki<-rbind(long_wikipedia_data,long_forecast_ets_wiki,long_forecast_hierarchy_ets_wiki)

long_forecast_ets_split_wiki<-split.data.frame(long_forecast_ets_wiki,long_forecast_ets_wiki$category)
sample_series_ets_wiki<-rbind.data.frame(long_forecast_ets_split_wiki[[1]],long_forecast_ets_split_wiki[[100]],long_forecast_ets_split_wiki[[200]],long_forecast_ets_split_wiki[[300]],long_forecast_ets_split_wiki[[400]], long_forecast_ets_split_wiki[[500]]
                                    )

ggplot(sample_series_ets_wiki, aes(x = Time, y = views, color = Method)) + geom_line(size=1) + 
  scale_colour_manual(values=c(validation='black', ets='blue', Hierarchy_ets='green'))+
  facet_wrap( ~ category, ncol = 3,scales = 'free')+theme(text  = element_text(size = 12),legend.direction = "horizontal",
    legend.position = "bottom")
```

## Comparing OLS methods - with and without hierarchy - log(RMSE) Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot log(RMSE)
ggplot() +
  geom_density(data = Long_RMSE_OLS_wiki, aes(x = (RMSE), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-10, 10)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing OLS methods - with and without hierarchy - log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot log(RMSE)
ggplot() +
  geom_boxplot(data = Long_RMSE_OLS_wiki,
               aes(x = Method, y = (RMSE), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing OLS methods - with and without hierarchy - Subtracted log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
RMSE_OLS_wiki<-RMSE_OLS_wiki[match(rownames(RMSE_OLS_wiki), rownames(RMSE_hierarchy_OLS_wiki)), ]
subtract_hierarchy_OLS_OLS_RMSE_wiki<-as.data.frame(RMSE_OLS_wiki$RMSE - RMSE_hierarchy_OLS_wiki$RMSE)
subtract_hierarchy_OLS_OLS_RMSE_wiki$Method<-"Sub-Hierarchy-OLS-OLS-RMSE"
names(subtract_hierarchy_OLS_OLS_RMSE_wiki)<-c("sublog(RMSE)","Method")

ggplot() +
  geom_boxplot(data = subtract_hierarchy_OLS_OLS_RMSE_wiki,
               aes(x = Method , y = (subtract_hierarchy_OLS_OLS_RMSE_wiki$`sublog(RMSE)`), 
                   fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing OLS methods - with and without hierarchy - Error Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot Error
ggplot() +
  geom_density(data = Long_Error_OLS_wiki , aes(x = (Error), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-40, 40)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing OLS methods - with and without hierarchy - Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot Error
ggplot() +
  geom_boxplot(data = Long_Error_OLS_wiki,
               aes(x = Method, y = (Error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing OLS methods - with and without hierarchy - Subtracted Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
cols_OLS_OLS_hierarchy_wiki <- sort(intersect(names(error_OLS_wiki), names(error_hierarchy_OLS_wiki)))
subtract_OLS_OLS_hierarchy_wiki<-error_OLS_wiki[cols_OLS_OLS_hierarchy_wiki] - error_hierarchy_OLS_wiki[cols_OLS_OLS_hierarchy_wiki]
long_subtract_OLS_OLS_hierarchy_wiki<-melt(subtract_OLS_OLS_hierarchy_wiki)
long_subtract_OLS_OLS_hierarchy_wiki$Method<-"Sub-OLS-hierarchy-OLS"
names(long_subtract_OLS_OLS_hierarchy_wiki)<-c("Series","subtracted_error","Method")

ggplot() +
  geom_boxplot(data = long_subtract_OLS_OLS_hierarchy_wiki,
               aes(x = Method, y = (subtracted_error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Subtracted-Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing ets methods - with and without hierarchy - Forecasted Series Plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE, fig.width=8.3, fig.height=5}
long_forecast_OLS_wiki<-rbind(long_wikipedia_data,long_forecast_OLS_wiki,long_forecast_hierarchy_OLS_wiki)

long_forecast_OLS_split_wiki<-split.data.frame(long_forecast_OLS_wiki,long_forecast_OLS_wiki$category)
sample_series_OLS_wiki<-rbind.data.frame(long_forecast_OLS_split_wiki[[1]],long_forecast_OLS_split_wiki[[100]],long_forecast_OLS_split_wiki[[200]],long_forecast_OLS_split_wiki[[300]],long_forecast_OLS_split_wiki[[400]],long_forecast_OLS_split_wiki[[500]]
                                    )

ggplot(sample_series_OLS_wiki, aes(x = Time, y = views, color = Method)) + geom_line(size=1) + 
  scale_colour_manual(values=c(validation='black', OLS='blue', Hierarchy_OLS='green'))+
  facet_wrap( ~ category, ncol = 3,scales = 'free')+theme(text  = element_text(size = 12),legend.direction = "horizontal",
    legend.position = "bottom")
```

## WikipediaData: Comparing all methods - with and without hierarchy - log(RMSE) Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot log(RMSE)
ggplot() +
  geom_density(data = Long_RMSE_all_wiki, aes(x = (RMSE), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-10, 10)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing all methods - with and without hierarchy - log(RMSE) Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot log(RMSE)
ggplot() +
  geom_boxplot(data = Long_RMSE_all_wiki,
               aes(x = Method, y = (RMSE), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("log(RMSE)") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing all methods - with and without hierarchy - Error Density plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
#### density plot Error
ggplot() +
  geom_density(data = Long_Error_all_wiki , aes(x = (Error), fill = Method), alpha =
                 0.4) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() + xlim(c(-40, 40)) +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing all methods - with and without hierarchy - Error Boxplot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE}
###### boxplot Error
ggplot() +
  geom_boxplot(data = Long_Error_all_wiki,
               aes(x = Method, y = (Error), fill = Method),
               alpha = 0.5) +
  xlab("Method") + ylab("Error") +
  guides(fill = guide_legend(nrow = 1, bycol = TRUE)) +
  theme_bw() +
  theme(
    text  = element_text(size = 12),
    legend.direction = "horizontal",
    legend.position = "bottom"
  )
```

## WikipediaData: Comparing all methods - with and without hierarchy - Forecasted Series Plot

```{r echo=FALSE, results='hide',message=FALSE,warning=FALSE,cache=TRUE, fig.width=8.3, fig.height=5}
long_forecast_all_wiki<-rbind(long_wikipedia_data,long_forecast_arima_wiki,long_forecast_ets_wiki,long_forecast_OLS_wiki,                         long_forecast_hierarchy_arima_wiki,long_forecast_hierarchy_ets_wiki,long_forecast_hierarchy_OLS_wiki)

long_forecast_all_split_wiki<-split.data.frame(long_forecast_all_wiki,long_forecast_all_wiki$category)
sample_series_all_wiki<-rbind.data.frame(long_forecast_all_split_wiki[[1]],long_forecast_all_split_wiki[[100]],long_forecast_all_split_wiki[[200]],long_forecast_all_split_wiki[[300]],long_forecast_all_split_wiki[[400]], long_forecast_all_split_wiki[[500]]
                                    )

ggplot(sample_series_all_wiki, aes(x = Time, y = views, color = Method)) + geom_line(size=1) + 
  scale_colour_manual(values=c(validation='black', arima='blue', ets='green',OLS='red',Hierarchy_arima='pink',Hierarchy_ets='yellow',Hierarchy_OLS='brown'))+
  facet_wrap( ~ category, ncol = 3,scales = 'free')+theme(text  = element_text(size = 12),legend.direction = "horizontal",
    legend.position = "bottom")

```



